---
title: "cluster analysis"
output: html_document
---

genreate multiple crytocurrncy data

1. genreating data from the cryptor package


2. compare to bitcoin dataset from blockchain

```{r}
library(readr)
BTC_block <- read_csv("~/software/market-price (1).csv")
```

3. compare to coindesk bitcoin prices

```{r}
library(readr)
BTC_coindesk <- read_csv("~/software/coindesk-bpi-USD-close_data-2010-07-17_2018-04-23.csv")
View(coindesk_bpi_USD_close_data_2010_07_17_2018_04_23)
```



for simplicity I plan to work from 2014 forward.only use top 15 rank


```{r}
library(ggplot2)
library(dplyr)

will_i_get_rich$date <- as.Date(will_i_get_rich$date)

data<- subset(will_i_get_rich, will_i_get_rich$date >= "2014-01-01")

data <- subset(data,data$ranknow < 16)

```


generate plot of all data

```{r}
library(ggplot2)

ggplot(data) + 
  geom_line(aes(x=date, y=close,colour = name)) + ggtitle("Closing Price of Top 15 Cryptocurrencies", subtitle = "USD")

```


graph subset by rank

```{r}
ggplot(subset(data,ranknow == 1)) + 
  geom_line(aes(x=date, y=close, colour = slug)) 

```

```{r}
View(decompose)
```

```{r}
ggplot(bitcoin) + 
  geom_line(aes(x=date, y=close)) 
```

function to return decomposed time series data

```{r}

tsplot <- function(coin,year1,day1,year2,day2,aorm) {
#example tsplot("Bitcoin",2014,1,2018,1,"additive")
library(dplyr)  
cyp <- filter(data, name == coin) 
cyp <-subset(cyp, select = c(close))
ts <-  ts(cyp, start=c(year1,day1), end=c(year2,day2), frequency=365)
decompose = decompose(ts, aorm)



plot(as.ts(decompose$seasonal))
plot(as.ts(decompose$trend))
plot(as.ts(decompose$random))
plot(decompose)

}
```


```{r}
tsplot("Bitcoin",2014,1,2018,1,"multiplicative")
```

```{r}

stlplot <- function(coin,year1,day1,year2,day2) {
  
cyp <- filter(data, name == coin) 
cyp <-subset(cyp, select = c(close))
ts = ts(cyp, start=c(year1,day1), end=c(year2,day2), frequency = 365)
stl= stl(ts, "periodic")
seasonal_stl   <- stl$time.series[,1]
trend_stl      <- stl$time.series[,2]
random_stl     <- stl$time.series[,3]
 
plot(ts)
plot(as.ts(seasonal_stl))
plot(trend_stl)
plot(random_stl)
plot(stl)

}


```

```{r}
stlplot("Bitcoin",2014,1,2018,112)
```

See that there is seasonal variations peaking around december months. 

Will peform stl function with number of transcations per day data from blockchain

```{r}
library(readr)
bitcoin_transactions <- read_csv("~/software/n-transactions (1).csv")

bitcoin_transactions$`2009-01-03 00:00:00` <- as.Date(bitcoin_transactions$`2009-01-03 00:00:00`, format="%Y-%m-%d")

bitcoin_transactions <- subset(bitcoin_transactions, bitcoin_transactions$`2009-01-03 00:00:00` >= "2014-01-01")

```


code to graph
```{r}
stlblockchain <- function (data,year1,day1,year2,day2) {


cyp <- data[,2]
ts = ts(cyp, start=c(year1,day1), end=c(year2,day2), frequency = 183)
stl= stl(ts, "periodic")
seasonal_stl   <- stl$time.series[,1]
trend_stl      <- stl$time.series[,2]
random_stl     <- stl$time.series[,3]
 
plot(ts)
plot(as.ts(seasonal_stl))
plot(trend_stl)
plot(random_stl)
plot(stl)

}
```


```{r}
stlblockchain(bitcoin_transactions,2014,1,2018,110)
```




