---
title: "Intro"
output: html_document
---

The bulk of my data was derived from the CryptoR package. 

Documentation avalible at https://cran.r-project.org/web/packages/crypto/index.html

```{r, eval=FALSE}
install.packages("crypto")
library(crypto)

will_i_get_rich <- getCoins()

# Get list of coins and rank
rich_list <- listCoins()
```

In order to verify the validity/consistency of the data, I will compare the the bitcoin vaule retrived from the CryptoR package with that that was collected from the following. Downloads are available at the supplied URLS.

Blockchain.info
https://blockchain.info/charts/market-price?timespan=all

```{r, eval=FALSE}
library(readr)
BTC_block <- read_csv("~/software/market-price (1).csv")
```

Coindesk
https://www.coindesk.com/price/

```{r, eval=FALSE}
library(readr)
BTC_coindesk <- read_csv("~/software/coindesk-bpi-USD-close_data-2010-07-17_2018-04-23.csv")
```


With an eyeball comparison to make sure the data checks out we proceed with most of our work concerning the dataset generated from the crypto package.  

```{r}
str(will_i_get_rich)

```

I decide that I would focus on the top 15 cryptocurrencies. This top 15 ranking is determined by a varible generated in cryptoR called ranknow. This ranking was scrapped from CoinMarketCoin.Com and is an indictor of Market Cap.


Range of Cryptocurrencies, also telling us the amount of cryptocurrencies in the dataset. 
```{r}
range(will_i_get_rich$ranknow)
```


Names of the Top 15 Cryptocurrencies
```{r}
library(dplyr)

will_i_get_rich %>% select(name,ranknow) %>% filter (ranknow < 16) %>% distinct(name,ranknow)

```

I decided to partition the data based on the top 15 Cryptocurrencies and all after 2014. 

```{r}
library(ggplot2)
library(dplyr)

will_i_get_rich$date <- as.Date(will_i_get_rich$date)

data<- subset(will_i_get_rich, will_i_get_rich$date >= "2014-01-01")

data <- subset(data,data$ranknow < 16)
```

This partitioned dataset will be known as "data"

```{r}
str(data)
```

Plot of entire dataset

```{r}
library(ggplot2)

ggplot(data) + 
  geom_line(aes(x=date, y=close,colour = name)) + ggtitle("Closing Price of Top 15 Cryptocurrencies", subtitle = "USD")

```


Graph of Market Closing Vaule in USD for the dominating outlier (Bitcoin)

```{r}
ggplot(subset(data,ranknow == 1)) + 
  geom_line(aes(x=date, y=close, colour = name)) 
```


Graph of Market Closing Vaule in USD for Top 15 Cryptocurrencies minus bitcoin 

```{r}
ggplot(subset(data,ranknow > 1)) + 
  geom_line(aes(x=date, y=close, colour = name)) 
```


Graph Market Closing Vaule in USD of 6-15 Top Cryptocurrencies

```{r}
ggplot(subset(data,ranknow > 5)) + 
  geom_line(aes(x=date, y=close, colour = name))
```





