---
title: "Intro"
output: html_document
---

The bulk of my data was derived from the CryptoR package. 

Documentation avalible at https://cran.r-project.org/web/packages/crypto/index.html

```{r, eval=FALSE}
library(crypto)

will_i_get_rich <- getCoins()

# Retrieve crypto market history for specific coin
will_i_get_rich_from <- getCoins("kin")

# Get list of coins and rank
rich_list <- listCoins()
```

In order to verify the validity/consistency of the data, I will compare the the bitcoin vaule retrived from the CryptoR package with that that was collected from the following. Downloads are available at the supplied URLS.

Blockchain.info
https://blockchain.info/charts/market-price?timespan=all

```{r, eval=FALSE}
library(readr)
BTC_block <- read_csv("~/software/market-price (1).csv")
```

Coindesk
https://www.coindesk.com/price/

```{r, eval=FALSE}
library(readr)
BTC_coindesk <- read_csv("~/software/coindesk-bpi-USD-close_data-2010-07-17_2018-04-23.csv")
```


With an eyeball comparison to make sure the data checks out we proceed with most of our work concerning the dataset generated from the crypto package.  


I decide that I would focus on the top 15 cryptocurrencies. This top 15 ranking is determined by a varible generated in cryptoR called ranknow. This ranking was scrapped from CoinMarketCoin.Com and is an indictor of Market Cap.

```{r}
str(will_i_get_rich)
```


```{r}
library(dplyr)

will_i_get_rich %>% select(name,ranknow) %>% filter (ranknow < 16) %>% distinct(name,ranknow)

```


```{r}
library(ggplot2)
library(dplyr)

will_i_get_rich$date <- as.Date(will_i_get_rich$date)

data<- subset(will_i_get_rich, will_i_get_rich$date >= "2014-01-01")

data <- subset(data,data$ranknow < 16)
```



